UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-10 files/paper/paper.tex
updates

\subsection{Adversarial Networks}
GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator network competes against an adversary.
Given an image $I^D$, the generator is trained to produce an image to try and fool the discriminator, which is trained to distinguish be between distorted
and non-distorted underwater images. In the original GAN formulation, the goal is to solve the minimax problem: \newline

@@

\noindent Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, the discriminator
is hypothesized as a classifier with a sigmoid cross entropy loss function,
which in practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
hypothesize a different loss function for the discriminator \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}.
We focus on the Wasserstein GAN (WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}. In this formulation, $W$ is
approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To ensure $f$ is $k$-Lipschitz, the weights of the discriminator
are clipped to some range $[-c, c]$. In our work, we adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of
clipping network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft constraint on the
gradient norm of the discriminator's output with respect to its input. Following \cite{gulrajani2017improved}, the new objective then becomes

\begin{equation}
\begin{aligned}
   \mathcal{L}_{WGAN} = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
\end{aligned}
\end{equation}

@@

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN} = \mathcal{L}_{WGAN} + \mathcal{L}_{L1}.
   \end{aligned}
\end{equation}

@@

\noindent In our experiments, we denote our network as UGAN-D when considering the GDL, which can be expressed as

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN-D} = \mathcal{L}_{WGAN} + \mathcal{L}_{L1} + \mathcal{L}_{GDL}.
   \end{aligned}
\end{equation}

\subsection{Network Architecture and Training Details}
We use a similar architecture as \cite{isola2016image}. Due to the Our generator is a U-Net
L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.

>>>>

\subsection{Adversarial Networks}
GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator
network competes against an adversary. Conditioned on an image $I^D$, the generator is trained to produce an \
image to try and fool the discriminator, which is trained to distinguish be between distorted and non-distorted
underwater images. In the original GAN formulation, the goal is to solve the minimax problem: \newline

@@

\noindent Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, the discriminator
is hypothesized as a classifier with a sigmoid cross entropy loss function,
which in practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
hypothesize a different loss function for the discriminator \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}.
We focus on the Wasserstein GAN (WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}. In this formulation, $W$ is
approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To ensure $f$ is $k$-Lipschitz, the weights of the discriminator
are clipped to some range $[-c, c]$. In our work, we adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of
clipping network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft constraint on the
gradient norm of the discriminator's output with respect to its input. Following \cite{gulrajani2017improved}, our new objective then becomes

\begin{equation}
\begin{aligned}
   \mathcal{L}_{WGAN}(G,D) = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
\end{aligned}
\end{equation}

@@

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \mathcal{L}_{L1}(G).
   \end{aligned}
\end{equation}

@@

\noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \mathcal{L}_{L1}(G) + \mathcal{L}_{GDL}
   \end{aligned}
\end{equation}

\subsection{Network Architecture and Training Details}
We use an encoder-decoder network similar to the work of \cite{isola2016image}, in which our generator is
structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.

``U-Net''

L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
